Supplementary Materials

### 2023-03-31 manuscript/supplementary.tex
minor ms changes
ms updates

\begin{align}
  \label{suppeqn:b}
  B(x, \Psi) = \exp \left( \sum_g^S \sum_{i} b\left( \mu_{i, \;k(g)}, s_i, L_g, r_g, d(x, g) \right)\right)
\end{align}

@@

In practice, to fit such a model, we must discretize both $\mu(s, k(g))$ and
$s$. Our models use a fixed $m_s$-element grid of selection coefficients, and
mutation rates are on a fixed $m_\mu$-element grid, which is later interpolated
over during the maximum likelihood optimization. The number of annotation
features $K$ is variable and set by the annotation data specified. There are
two ways to parameterize the mutation rates and DFE for all annotation classes
in background selection models. First, for the \emph{free-mutation}
parameterization, each annotation feature class has a free mutation rate
parameter for each of these selection coefficients (as in equation
\eqref{suppeqn:b}).

@@

\printbibliography

>>>>

In practice, to fit such a model, we must discretize both $\mu(s, k(g))$ and
$s$ in Equation \eqref{suppeqn:b}. We define $\mu_i$ to be the rate of
mutations entering the population per basepair, per generation with selection
coefficient $s_i$ (i.e. the product of the mutation rate and the distribution
of deleterious fitness effects). Then, the reduction at position $x$ is,

\begin{align}
  \label{suppeqn:b}
  B(x, \Psi) = \exp \left( \sum_g^S \sum_{i} b\left( \mu_{i, \;k(g)}, s_i, L_g, r_g, d(x, g) \right)\right).
\end{align}

@@

Because it is computationally-intensive to numerically solve the system of two
non-linear equations to calculate $b$ at each segment, these are pre-computed
for an $m_s$-element grid of selection coefficients and an $m_\mu$-element grid
of mutation rates--DFE products. The number of annotation features $K$ is
variable and set by the annotation data specified. There are two ways to
parameterize the mutation rates and DFE for all annotation classes in
background selection models. First, for the \emph{free-mutation}
parameterization, each annotation feature class has a free mutation rate
parameter for each of these selection coefficients (as in equation
\eqref{suppeqn:b}).

@@

\subsection{Numeric Optimization}

mu bounds

bounds and time, bounds and convergence

Same optima, but took longer

%Our $B$ is,
%
%\begin{align}
%  B = \frac{1}{2N} \sum_{t=0}^\infty \prod_{i=0}^t \left(1 - \frac{1}{2N_e(i)}\right).
%\end{align}
%
%This sum takes many terms to converge, which makes calculating the $B$ between
%each focal neutral site and segment intractably slow (even when the equilibrium
%$\widetilde{V}$ for the segment pre-calculated). We approximate this in the
%following way for faster numerical calculations. Let $g(t) = \prod_{i=0}^t (1 -
%\nicefrac{1}{2N_e(i)})$. Then, taking the first-order series expansion around
%the logarithm of the terms and approximating the sum with an integral,
%
%\begin{align}
%  g(t) &\approx \exp\left(- \frac{1}{2N} \int_0^t \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) 
%       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
%\end{align}
%
%$B$ is the case of $\lim b \to \infty$ for $B(b)$. Approximating the sum in
%$B(b)$ with an integral,
%
%\begin{align}
%  B(b) &= \int_0^b \exp\left(- \frac{1}{2N} \int_0^t \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) dt \\
%       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
%\end{align}
%
%Now, let $z = \log(t)$, then
%
%\begin{align}
%  B(w) &= \int_0^w \exp\left(- \frac{1}{2N} \int_0^{\log(z)} \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) \exp(t) dz \\
%       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
%\end{align}
%
%
\printbibliography
